Template Master's Thesis

### 2023-08-21 paper.tex
Add section to analysis, add potential conclusion contentsl

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../figures/land_network.png}
	\caption{LAND token network}
	\label{fig:LAND_network}
\end{figure}

@@

Combining the results of self-authorization, learned node embedding and LAND transfers, we can cluster 37.5\% (51,581 out of 137,544) of addresses representing 29,680 entities. \newline
We assume that the unclustered addresses each represent individual entities, a (strict) distance threshold of 0.5 for clustering addresses generated by Role2Vec and remove the 71-address cluster found in self-authorization.
We estimate a total of 115,643 active users during the studied time frame. Among them, 8,483 entities (X \%) interacted with Decentraland through more than one address. The largest entity consists of 499 addresses. The distribution of cluster sizes can be seen in Figure \ref{fig:barplot_clusters}.

@@

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=0.65\textwidth]{../figures/land_network.png}
	\caption{LAND token network}
	\label{fig:LAND_network}
\end{figure}

@@

To conclude our clustering analysis, we combine the results of self-authorization, learned node embedding and LAND transfer heuristics. By doing so, we can cluster 51,581 out of 137,544 (37.5\%) addresses that represent 29,680 entities. 
For the remaining addresses, we consider each as an individual entity. 
We applied a strict distance threshold of 0.5 for clustering embeddings generated by Role2Vec and excluded the 80-address cluster identified in self-authorization.
Under these assumptions, we estimate 115,643 active users during the time frame studied. Out of these, 8,483 entities (7.3\%) interacted with Decentraland through multiple addresses. The largest entity comprises 499 addresses. We plot the distribution of cluster sizes in Figure \ref{fig:barplot_clusters}.

@@

1. Public blockchain -> all data available -> allows us to analyse it and find information
2. Clustering heuristics for account-based blockchains using on-chain data and on specific predefined address set
3. Most successful graph representation learning because does not require participation in specific on-chain event / usage pattern
4. From the various methods Role2Vec best
5. Summarize Final results
6. For researchers -> extend this approach -> apply it to other address sets -> package
7.
